Music Recommendation System Using the Million Song Dataset

### 2015-05-07 writeup/MSDgroupwriteup.tex
updates
plots

- Sparsity .0016086
-

@@

\subsection{Testing}
We tested our algorithms against each other using a mean average precision 
score for each method.  The mean average precision (MAP) calculation came directly from the Kaggle MSD challenge \citep{kaggleMSD}. The score was used to rank the competition entries.

@@

\hline
\bf{Algorithm} &  \bf{MAP score}\\ \hline
Artist Based Popularity Baseline  & 0.0448    \\ 
%\hline
Top 500 Songs by Count  Baseline &  0.0138  \\ 
%\hline
Top 500 Songs by Plays  Baseline &  0.0126  \\ 
%\hline
User Based  CF  &  0.0377 \\ 
%\hline
Item Based  CF  &  0.0479 \\ 
%\hline
Matrix Factorization  &   0.0143  \\ 
%\hline
\end{tabular}
\end{center}
\end{table}

>>>>

@@

\subsection{Testing}
We tested our algorithms against each other using a mean average precision 
score for each method.  The mean average precision (MAP) calculation came directly from the Kaggle MSD challenge \citep{McFee:2012:MSD:2187980.2188222}. The score was used to rank the competition entries.

@@

\hline
\bf{Algorithm} &  \bf{MAP score}\\ \hline
Item Based  CF  &  0.0479 \\ 
Artist Based Popularity Baseline  & 0.0448    \\ 
User Based  CF  &  0.0377 \\ 
Matrix Factorization  &   0.0143  \\ 
Top 500 Songs by Count  Baseline &  0.0138  \\ 
Top 500 Songs by Plays  Baseline &  0.0126  \\ 
\end{tabular}
\end{center}
\end{table}
